\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} 
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{#1 \vspace{-2pt}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape John Doe} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:johndoe@example.com}{\underline{johndoe@example.com}} $|$ 
    \href{https://linkedin.com/in/johndoe}{\underline{https://linkedin.com/in/johndoe}} $|$
    \href{https://github.com/johndoe}{\underline{https://github.com/johndoe}}
\end{center}
\section{Education}
\resumeSubHeadingListStart

	\resumeSubheading{Bachelor of Science in Computer Science}{Sept 2018 -- June 2022}{University of Example}{Example City, EX}

	\resumeSubheading{Master of Science in Data Science}{Sept 2023 -- Present}{Example Institute of Technology}{Example City, EX} \resumeSubHeadingListEnd\section{Extracurriculars}
\resumeSubHeadingListStart

	\resumeSubheading{Volunteer Teacher}{Jan 2020 -- Dec 2020}{Code for Good}{Example Community Center}
	\resumeItemListStart
			\resumeItem{Taught basic programming to underprivileged youth.}
			\resumeItem{Organized weekly coding workshops.}
		\resumeItemListEnd

	\resumeSubheading{Club President}{Sept 2019 -- June 2021}{University Coding Club}{University of Example}
	\resumeItemListStart
			\resumeItem{Led a team of 20 members to organize hackathons and coding bootcamps.}
			\resumeItem{Increased club membership by 50\%.}
		\resumeItemListEnd \resumeSubHeadingListEnd\section{Projects}
\resumeSubHeadingListStart

	\resumeSubheading{Personal Portfolio Website}{Feb 2021 -- April 2021}{Self-Initiated}{https://portfolio.example.com}
	\resumeItemListStart
			\resumeItem{Built a responsive personal portfolio website using HTML, CSS, and JavaScript.}
			\resumeItem{Showcases projects, skills, and contact information.}
		\resumeItemListEnd

	\resumeSubheading{Data Analysis Pipeline}{June 2022 -- Aug 2022}{Data Science Internship}{https://github.com/example/data-analysis-pipeline}
	\resumeItemListStart
			\resumeItem{Developed a data analysis pipeline to clean, process, and visualize large datasets.}
			\resumeItem{Reduced data processing time by 30\%.}
		\resumeItemListEnd \resumeSubHeadingListEnd\section{Experiences}
\resumeSubHeadingListStart

	\resumeSubheading{Software Engineer Intern}{May 2021 -- Aug 2021}{Tech Solutions Inc.}{Example City, EX}
	\resumeItemListStart
			\resumeItem{Developed a REST API to manage user data, reducing response time by 25\%.}
			\resumeItem{Collaborated with the frontend team to integrate backend services.}
		\resumeItemListEnd

	\resumeSubheading{Junior Developer}{Sept 2022 -- May 2023}{InnovateX}{Example City, EX}
	\resumeItemListStart
			\resumeItem{Maintained and optimized e-commerce platform, improving page load speed by 40\%.}
			\resumeItem{Automated recurring tasks, saving the team 10 hours per week.}
		\resumeItemListEnd \resumeSubHeadingListEnd\section{Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
        \small{\item{
		\textbf{Languages}: Python, Java, C++ \\ 
		\textbf{Frameworks}: Django, React \\ 
		\textbf{Developer Tools}: Git, Docker, VS Code \\ 
		\textbf{Other Skills}: SQL, Machine Learning}}
        \end{itemize}\end{document}